QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-01 Revision/Paper_Rev.tex
Rev_V3.0

\subsection{QoE Function}
The QoE function evaluates the influence of agent's actions by taking several key performance factors into account. Given the selected action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$, we represent $\mathcal{D}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$ as the delay of task $z_i(t),$ which indicates the number of time slots from time slot $t$ to the time slot in which task $z_i(t)$ is processed. It is calculated by: \vspace{2mm}

@@

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
\hspace{1.8cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}
Given the delay and energy consumtion of task $z_i(t)$, we also define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$. \vspace{1.7mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. When the MD is operating in performance mode, the primary focus is on minimizing task delays, thus the delay contributes more to the cost. On the other hand, when the MD switches to ultra power-saving mode, the main attention is directed toward reducing power consumption.

@@

>>>>

\newpage.\newpage

\subsection{QoE Function}
\textcolor{brown}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. When the MD is operating in performance mode, the MD's preference is to minimize task delays. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption.
Based on the system model, we first formulate the calculation of task delay, energy consumption, and associated cost, and then represent the QoE function accordingly.}

Given the selected action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$, we represent $\mathcal{D}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$ as the delay of task $z_i(t),$ which indicates the number of time slots from time slot $t$ to the time slot in which task $z_i(t)$ is processed. It is calculated by: \vspace{2mm}

@@

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
\hspace{1.8cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}

Given the delay and energy consumtion of task $z_i(t)$, we also define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$. \vspace{1.7mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. When the MD is operating in performance mode, the delay contributes more to the cost than energy consumption. Otherwise, when the MD switches to ultra power-saving mode, the energy consumption contributes more to the cost than delay due to main attention on reducing power consumption.

@@

\newpage.\newpage
